Generating Datasets about Building Designs \\Based on a Multilayer Building Ontology

### 2015-04-29 article-00-headers.tex
Changed Principle style

\spnewtheorem{principle}{Principle}{\bfseries}{\rmfamily}

@@

@@

% ifcOWL layer names
\newcommand{\simple}{\textbf{Simple}}
\newcommand{\standard}{\textbf{Standard}}
\newcommand{\extended}{\textbf{Extended}}

\newcommand{\ifcowl}{\textbf{ifcOWL}}
\newcommand{\ifcsimple}{\ifcowl{}-\simple{}}
\newcommand{\ifcstandard}{\ifcowl{}-\standard{}}
\newcommand{\ifcextended}{\ifcowl{}-\extended{}}
\newcommand{\ifcrdf}{\textbf{ifcRDF}}

>>>>

%\spnewtheorem{principle}{Principle}{\bfseries}{\rmfamily}

\AtBeginDocument{
    \newtheoremstyle{principleStyle}
        {1.5\topsep} % Space above, default \topsep
        {\topsep} % Space below, default \topsep
        {\itshape} % Body font
        {} % Indent amount, example: \parindent
        {\bfseries\itshape} % Theorem head font
        {.} % Punctuation after theorem head
        {.5em} % Space after theorem head
        {} % Theorem head spec (can be left empty, meaning `normal')

    \theoremstyle{principleStyle} \newtheorem{principle}{Principle}
}

@@

%
% THEOREMS
%
\usepackage{amsthm}

@@

% ifcOWL layer names
\newcommand{\simple}{\textnormal{\textbf{Simple}}}
\newcommand{\standard}{\textnormal{\textbf{Standard}}}
\newcommand{\extended}{\textnormal{\textbf{Extended}}}

\newcommand{\ifcowl}{\textnormal{\textbf{ifcOWL}}}
\newcommand{\ifcsimple}{\ifcowl{}-\simple{}}
\newcommand{\ifcstandard}{\ifcowl{}-\standard{}}
\newcommand{\ifcextended}{\ifcowl{}-\extended{}}
\newcommand{\ifcrdf}{\textbf{ifcRDF}}
